Proposal: Translation of B Implementations to LLVM-IR

### 2013-08-22 PAPERS/2013-SBMF/paper_short.tex

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xspace,framed,here,keystroke}
\pagestyle{headings}
\title{A Proposed Translation of B Implementations to the LLVM}
\author{David D\'{e}harbe \inst{1} \and Val\'{e}rio Medeiros Jr.\inst{2}}
\institute{Federal University of Rio Grande do Norte, UFRN, Brazil\\
\and 
Federal Institute of Education, Science and Technology  of Rio Grande do Norte, IFRN, Brazil}
\date{May 2013}

@@

\begin{abstract}
The aim of this work is to lay the foundations of a multi-platform code
generator for the B method. In particular, this paper presents a proposed
translation  procedure from a subset of the B language for implementations
towards LLVM source code. This translation is defined formally as a set of
rules defined recursively on the abstract syntax for B implementations. It 
presents a overview of translation and a simplified example.
\end{abstract}

@@

Operations and instructions are translated to LLVM instructions as discussed in
sec.~\ref{sec:control}. For reason of reduced space, only the operations and
instructions will be presented with more details.

@@

This paper presents the formal specification of a translation from a large
subset of the B implementation language to LLVM, a modern compiler internal
language.  Even though this is still a work in progress, the definition is
self-contained and has a large enough scope to be applied to B implementations
where the data belongs to basic types. This specification is a blueprint for a
code synthesis tool for B that is currently being implemented. This tool will be
distributed as an extension to Atelier-B under an open-source license.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xspace,framed,here,keystroke}
\pagestyle{headings}
\title{Proposal: Translation of B Implementations to LLVM-IR}
\author{David D\'{e}harbe \inst{1} \and Val\'{e}rio Medeiros Jr.\inst{2}}
\institute{Federal University of Rio Grande do Norte, UFRN, Brazil\\
\and 
Federal Institute of Education, Science and Technology  of Rio Grande do Norte, IFRN, Brazil}
\date{May 2013}

@@

\begin{abstract}
The aim of this work is to lay the foundations of a multi-platform code
generator for the B method. In particular, this paper presents a proposed
translation  procedure from a subset of the B language for implementations
towards LLVM source code. This translation is defined formally as a set of
rules defined recursively on the abstract syntax for B implementations. It 
presents an overview of translation and a simplified example.
\end{abstract}

@@

Operations and instructions are translated to LLVM instructions as discussed in
sec.~\ref{sec:control}. For a reason of reduced space, only the operations and
instructions will be presented with more details.

@@

This paper presents the formal specification of a translation from a subset of
the B implementation language to LLVM, a modern compiler internal language.
Even though this is still a work in progress, the definition is self-contained
and has a large enough scope to be applied to B implementations where the data
belongs to basic types. This specification is a blueprint for a code synthesis
tool for B that is currently being implemented. This tool will be distributed
as an extension to Atelier-B under an open-source license.
